MSCA 31006: Final Project - AQI Forecasting

### 2023-08-15 MSCA_31006_Time_Series_Final_Project - TBATS.Rmd
Add files via upload

# Compare the forecast with the actual test data by calculating MAPE and MSE
# Mean Absolute Percentage Error (MAPE)
mape_snaive <- mean(abs((test_monthly - forecast_snaive_monthly$mean)/test_monthly))
mape_snaive

@@

mae <- mean(abs(test_weekly - forecast_tbats$mean))
print(cat("Mean Absolute Error (MAE):", round(mae, 2), "\n"))
#Mean Absolute Error (MAE): 9.31

@@

>>>>

# Compare the forecast with the actual test data by calculating MAPE and MSE
mae_snaive_monthly <- mean(abs((test_monthly - forecast_snaive_monthly$mean)))
mae_snaive_monthly

# Mean Absolute Percentage Error (MAPE)
mape_snaive <- mean(abs((test_monthly - forecast_snaive_monthly$mean)/test_monthly))
mape_snaive

@@

mae <- mean(abs(test_weekly - forecast_tbats$mean))
print(cat("Mean Absolute Error (MAE):", round(mae, 2), "\n"))
#Mean Absolute Error (MAE): 9.31 
mape <- mean(abs(test - forecast_tbats$mean)/test * 100)
cat("Mean Absolute Percentage Error (MAPE):", round(mape, 2), "\n")

@@

model_tbats$lambda
model_tbats$alpha
model_tbats$beta
model_tbats$seasonal.periods
model_tbats$p
model_tbats$q
model_tbats$likelihood
model_tbats$AIC
